Notes

### 2021-02-08 supCLT-ind.tex

	Denote by $\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
$\mathcal{P}
  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.$
	Define
	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \},
		~
	\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
	$ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
	Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
	Define a semigroup
\begin{align}\label{e:Tt}
	T_t f
	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
	\quad t\geq 0, f\in \mathcal P,
	and a family of functionals
\begin{align}\label{eq:M.13}
	m_t[f]
	:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx,
	\quad 0 \leq t< \infty, f\in \mathcal P.
	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
\begin{equation} \label{eq:I:R:3}
\begin{minipage}{0.9\textwidth}
	for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,$ where
	m[f]
	:=
\begin{cases}
	\lim_{t\to \infty} m_t[f], &
	f \in \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l, \\
	\lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l.
\end{cases}
\end{minipage}
		For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
	We also proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
	\begin{equation}\label{eq:oldResult}
\begin{minipage}{0.9\textwidth}
	if $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb {\widetilde P}_\mu$,
\[
\begin{split}
	&e^{-\alpha t}\|X_t\| \xrightarrow[t\to \infty]{\text{a.s.}} \widetilde{H}_\infty;
	\quad \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s};
	\\&\frac{X_t(f_\mathrm c)}{\|t X_t\|^{1-\tilde \beta} } \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm c};
	\quad\frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
	\xrightarrow[t\to \infty]{d} \zeta^{-f_\mathrm l},
\end{split}
\]
	where $\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
	$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; and
\[
	\mathrm x_t(f)
	:= \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty},
	\quad t\geq 0, f\in \mathcal P.
\]
\end{minipage}
	The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
	A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$;
  and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero while $f_\mathrm c \equiv 0$.
	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem in this case. We conjectured there that the limit random variables in \eqref{eq:oldResult} for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
	Once this asymptotic independence is established, a central limit theorem  for $ X_t(f)$ for all $f\in  \mathcal P$ would follow.

@@

\section{Proof of main result}
\label{proofs of main results}
	We first make some preparations before proving Theorem \ref{thm:M}.
	For every $t\geq 0$ and $f\in \mathcal P$, define
\[
  	Z_t f
  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
  	\quad \Upsilon^f_t
   	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
\]
	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
the weak limit of $\Upsilon^f_t$.
	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
	The following Lemma \ref{lem:P:R} can be proved using 
an argument similar to that used in the proof of 
	\cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
\begin{lem}
\label{lem:P:R}
	For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
\end{lem}

@@

	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
	\begin{lem}
\label{ineq: analysis}
	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
\[
    |(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
    \leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
\]
\end{lem}
\begin{comment}
\begin{proof}
   	Note that
\[
  	\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}-1}{y^{\beta}}
  	=\lim_{|y|\rightarrow \infty}\frac{(y+1)^{1+\beta}-y^{1+\beta}}{y^{\beta}}
  	=\lim_{|y|\rightarrow \infty}\big((1+\frac{1}{y})^{1+\beta}-1\big)y = 1+\beta.
\]
	Using this and continuity, we get that there exists $C_1>0$ such that for all $|y|\geq 1$,
\[
  	|(1+y)^{1+\beta}-y^{1+\beta}-1|
  	\leq C_1 |y|^{\beta}.
\]
 	Note that if $x = 0$ or $y= 0$, then the desired result is trivial.
	So we only need to consider the case that $x \neq 0$ and $y \neq 0$.
 	In this case, if $|x|\geq |y|$, we have
\[
	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
	\leq |y|^{1+\beta}\bigg(\Big|\Big(1+\frac{x}{y}\Big)^{1+\beta}-\Big(\frac{x}{y}\Big)^{1+\beta}-1\Big|\bigg)
	\leq C_1|y||x|^{\beta};
\]
	and  if $|x|\leq |y|$, we have
\[
	|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
	\leq |x|^{1+\beta}\bigg( \Big| \Big(1+\frac{y}{x}\Big)^{1+\beta}-\Big(\frac{y}{x}\Big)^{1+\beta}-1\Big|\bigg)
	\leq C_1|x||y|^{\beta}.
\]
	Combining the above, we immediately get the desired result.
\end{proof}
\end{comment}

	In the remainder of this section, we  fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$,  $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$.
	For every $t\geq 1$, define
\begin{align}
	R(t)
	&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
        \\R'(t)
    &=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
        \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
\end{align}
where $T_k$ is the operator defined in 
\eqref{e:Tt}, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
	The following result is a special case of Theorem \ref{thm:M}.
\begin{thm}\label{thm: II}
	Under $\mathbb{\widetilde{P}}_{\mu}$, $R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
\end{thm}
\begin{proof}
	In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
	According to the proof of 
\cite[Theorem 1.6]{RenSongSunZhao2019Stable} and the fact that the convergence in
 probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
\[
	R(t)-R'(t)
	\xrightarrow[t\to \infty]{\text{in probability}} 0.
\]
	With the help of Slutsky's theorem, what is left to show is that,
\begin{equation} \label{lem:UOT}
	R'(t)
	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
\end{equation}

@@

  	\\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|

@@

	\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du - \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|

>>>>

	Denote by $\mathcal P \subset L^2(\varphi)$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,
$\mathcal{P}
  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.$
	Define
	$\mathcal C_\mathrm s := \mathcal P \cap \overline{\operatorname{Span}} \{ \phi_p: \alpha \tilde \beta < |p| b \},
		~
	\mathcal C_\mathrm c   := \mathcal P \cap \operatorname{Span} \{ \phi_p : \alpha \tilde \beta = |p| b \} $, and
	$ \mathcal C_\mathrm l   := \mathcal P \cap \operatorname{Span} \{ \phi_p: \alpha \tilde \beta > |p| b \}$.
	Note that $\mathcal C_\mathrm s$ is an infinite dimensional space, $ \mathcal C_\mathrm l$ and $\mathcal C_\mathrm c$ are finite dimensional spaces, and $\mathcal C_c$ might be empty.
	Define a semigroup
\begin{align}\label{e:Tt}
	T_t f
	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
	\quad t\geq 0, f\in \mathcal P,
\end{align}
	and a family of functionals
\begin{align}\label{eq:M.13}
	m_t[f]
	:= \eta \int_0^t \mathrm du \int_{\mathbb R^d} \big(-iT_u f(x)\big)^{1+\beta} \varphi(x) \mathrm dx,
	\quad 0 \leq t< \infty, f\in \mathcal P.
\end{align}
%{
	Let us explain the non-integer power of the complex numbers used above. 
	For each $z\in \mathbb C\setminus (-\infty, 0]$, we define $\log z : = \log |z| + i \arg z$ where $\arg z \in (-\pi,\pi)$ is uniquely determined so that $z = |z|e^{i \arg z}$. 
	For each $z\in \mathbb C\setminus (-\infty, 0]$ and $\gamma \in \mathbb R$, we define $z^\gamma := e^{\gamma \log z}$.
	For each $\gamma \geq 0$, we define $0^\gamma := \lim_{z\to 0, z\in \mathbb C\setminus (-\infty,0]} z^\gamma=\mathbf 1_{\gamma = 0}$.
%}

	We have shown in \cite[Lemma 2.6 and Proposition 2.7]{RenSongSunZhao2019Stable} that,
\begin{equation} \label{eq:I:R:3}
\begin{minipage}{0.9\textwidth}
	for each $f\in \mathcal P$, there exists a $(1+\beta)$-stable random variable $\zeta^f$ with characteristic function $\theta \mapsto e^{m[\theta f]}, \theta \in \mathbb R,$ where
\begin{equation}
	m[f]
	:=
\begin{cases}
	\lim_{t\to \infty} m_t[f], &
	f \in \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l, \\
	\lim_{t\to \infty} \frac{1}{t} m_t[f], & f\in \mathcal P \setminus \mathcal C_\mathrm s \oplus \mathcal C_\mathrm l.
\end{cases}
\end{equation}
\end{minipage}
\end{equation}
		For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$
	We also proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that
\begin{equation}\label{eq:oldResult}
\begin{minipage}{0.9\textwidth}
	if $\mu\in \mathcal M_\mathrm c(\mathbb R^d)\setminus \{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$, then under $\mathbb {\widetilde P}_\mu$,
\[
\begin{split}
	&e^{-\alpha t}\|X_t\| \xrightarrow[t\to \infty]{\text{a.s.}} \widetilde{H}_\infty;
	\quad \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}} \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s};
	\\&\frac{X_t(f_\mathrm c)}{\|t X_t\|^{1-\tilde \beta} } \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm c};
	\quad\frac{X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}
	\xrightarrow[t\to \infty]{d} \zeta^{-f_\mathrm l},
\end{split}
\]
	where $\widetilde H_\infty$ has the distribution of $\{H_{\infty}; \widetilde {\mathbb P}_\mu\}$;
	$\zeta^{f_\mathrm s}$, $\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}; and
\[
	\mathrm x_t(f)
	:= \sum_{p\in \mathbb Z^d_+:\alpha \tilde \beta>|p|b}\langle f,\phi_p\rangle_\varphi e^{(\alpha-|p|b)t}H^p_{\infty},
	\quad t\geq 0, f\in \mathcal P.
\]
\end{minipage}
\end{equation}
%{
	%The above result gives the central limit theorem for $X_t(f)$ if $f\in \mathcal P\setminus\{0\}$ satisfies $\alpha \tilde \beta \leq \kappa_f b$.
	%A general  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$;
  %and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm s$ and $f_\mathrm l$ maybe non-zero while $f_\mathrm c \equiv 0$.
	%In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem in this case. 
	Any  $f \in \mathcal P$ can be decomposed as $f_s + f_c + f_l$ with $f_s \in \mathcal C_\mathrm s$, $f_c \in \mathcal C_\mathrm c$ and $f_l \in \mathcal C_\mathrm l$. 
	In \cite{RenSongSunZhao2019Stable}, we were not able to establish a central limit theorem for $f$ if  $\|f_\mathrm s\|_{L^2(\varphi)}> 0, \|f_\mathrm c\|_{L^2(\varphi)} = 0$ and $\|f_\mathrm l\|_{L^2(\varphi)}> 0$.
%}	
	We conjectured there that the limit random variables in \eqref{eq:oldResult} for $f_\mathrm s\in \mathcal C_\mathrm s$, $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$ are independent.
	Once this asymptotic independence is established, a central limit theorem  for $ X_t(f)$ for all $f\in  \mathcal P$ would follow.

@@

%{
\begin{rem}
	We mention here that  the branching mechanism $\psi$ considered in this paper can be written in a form of $\psi(z)= -\alpha z + z^{1+\beta} (\eta + \epsilon(z))$ where $\epsilon (z) \to 0$ as $z \to 0$ (See \cite[Remark 1.3]{RenSongSunZhao2019Stable}).
	It would be interesting to consider the more general cases $\psi(z)= -\alpha z + z^{1+\beta}l(z)$ where $l(z)$ is only assumed to be a slowly varying function. 
	Note that in this case if $l$ blows up at $0$ (for example $l(z) = \log z$) our result can not hold anymore. 
	This is simply because the limiting $\alpha$-stable random variable $\zeta^f$ described in \eqref{eq:I:R:3} will cease to make sense. 
\end{rem}

%}

\section{Proof of main result}
\label{proofs of main results}
	We first make some preparations before proving Theorem \ref{thm:M}.
	For every $t\geq 0$ and $f\in \mathcal P$, define
\[
  	Z_t f
  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
  	\quad \Upsilon^f_t
   	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
\]
	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
the weak limit of $\Upsilon^f_t$.
	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
	The following Lemma \ref{lem:P:R} can be proved using 
an argument similar to that used in the proof of 
	\cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
\begin{lem}
\label{lem:P:R}
	%{
	%For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
	For any $g\in \mathcal P$ there exists non-negative $h \in \mathcal P$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
	%}
\end{lem}

@@

	The following analytic result is elementary, and will also be used in the proof of Theorem \ref{thm: II}.
\begin{lem} \label{ineq: analysis}
	There exists a constant $C>0$, such that for any $x,y \in \mathbb R$,
\[
%{
	%|(x+y)^{1+\beta}-x^{1+\beta}-y^{1+\beta}|
    |(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
    \leq C(|x||y|^{\beta}+|x|^{\beta}|y|).
    %}
\]
\end{lem}
%{
\begin{proof}
   	Note the desired result holds if $x =0$ or $y = 0$.
   	So, we can assume $|x|>0$ and $|y|>0$.
   	Noticing also the symmetry between $x$ and $y$, we can assume without loss of generality that $|x|\geq |y|$.
   	Also note that $\overline{ z^{1+\beta}} = \overline z^{1+\beta}$ for each $z \in \mathbb C \setminus (-\infty, 0)$ where $\bar z$ represents the conjugation of $z$.
   	So by taking conjugation, we can verify that 
\[
	|(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
	= |(-ix-iy)^{1+\beta}-(-ix)^{1+\beta}-(-iy)^{1+\beta}|.
\]
	This allows us to further assume without loss of generality that $y>0$.
	Now let us calculate that for each $z\in \mathbb C$, 
\begin{align}
  	&\lim_{r \to \infty, r>0}\frac{(r\pm 1)^{1+\beta}-r^{1+\beta} - z}{r^{\beta}}
  	=\lim_{r\to \infty, r > 0}\frac{(r\pm1)^{1+\beta}-r^{1+\beta}}{r^{\beta}}
  	\\&=\lim_{r\to \infty,r>0}\big((1\pm r^{-1})^{1+\beta}-1\big)r = \pm(1+\beta).
\end{align}
	Taking absolute value and using continuity, we get that for each $z\in \mathbb C$ there exists $C(z)>0$ such that for each $r\geq 1$,
\[
  	|(r\pm 1)^{1+\beta}-r^{1+\beta} - z|
  	\leq C(z) |r|^{\beta}.
\]
	For any $u\in \mathbb R\setminus\{0\}, r>0$ and $\gamma \geq 0$, from the fact that $\arg (iu r) = \arg(iu)+ \arg(r)$ we can verify $(iur)^{\gamma} = (iu)^{\gamma} r^{\gamma}$.
Therefore for each $r\geq 1$ we have
\begin{align}
	&\big|\big(i(1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big|
	= \big|i^{1+\beta} \big((r+1)^{1+\beta} - r^{1+\beta} - 1\big)\big|
	\\&= |(r+1)^{1+\beta}-r^{1+\beta}-1|
	\leq C(1) |r|^{\beta};
\end{align}
and for each $r\leq -1$ we have
\begin{align}
	&\big|\big( i (1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big|
	= \big|(-i)^{1+\beta} \big((-r - 1)^{1+\beta} - (-r)^{1+\beta} - i^{2+2\beta}\big)\big|
	\\&= |(-r-1)^{1+\beta}-(-r)^{1+\beta}  - i^{2+2\beta}|
	\leq C(i^{2+2\beta}) |r|^{\beta}.
\end{align}
	To summarize, there exists a $C_1>0$ such that for each $r\in \mathbb R$ with $|r|\geq 1$,
\[
	\big|\big( i(1+ r)\big)^{1+\beta} - (ir)^{1+\beta} - i^{1+\beta}\big| \leq C_1 |r|^\beta.
\]
	Now we can verify that
\begin{align}
	&|(ix+iy)^{1+\beta}-(ix)^{1+\beta}-(iy)^{1+\beta}|
	= \big|y^{1+\beta}\big(i(1+x/y)^{1+\beta}-(ix/y)^{1+\beta}- i^{1+\beta}\big)\big|
	\\&= |y|^{1+\beta}\big|\big(i(1+x/y)\big)^{1+\beta}-(ix/y)^{1+\beta}-i^{1+\beta}\big|
	\leq C_1|y||x|^{\beta}.
	\qedhere
\end{align}
\end{proof}
%}

	In the remainder of this section, we  fix $\mu \in \mathcal M_c(\mathbb R^d)\setminus\{0\}$, $f_\mathrm s\in \mathcal C_\mathrm s$,  $f_\mathrm c\in \mathcal C_\mathrm c$ and $f_\mathrm l\in \mathcal C_\mathrm l$.
	For every $t\geq 1$, define
\begin{align}
	R(t)
	&:=\Big( \frac{X_t(f_\mathrm s)}{\|X_t\|^{1-\tilde \beta}},\frac{X_t(f_\mathrm c)}{\|tX_t\|^{1-\tilde \beta}},\frac{ X_t(f_\mathrm l) - \mathrm x_t(f_\mathrm l)}{\|X_t\|^{1-\tilde \beta}}\Big),
        \\R'(t)
    %{
    %&=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
    &:=\big(R'_\mathrm s(t), R'_\mathrm c(t), R'_\mathrm l(t)\big)
    %}
        \\& :=\Big(\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_k \tilde f_\mathrm s},t^{\tilde \beta - 1}\sum_{k=0}^{\lfloor t-\ln t \rfloor} \Upsilon_{t-k-1}^{T_{k} \tilde f_\mathrm c},\sum_{k = 0}^{\lfloor t^2 \rfloor} \Upsilon_{t+k}^{- T_k \tilde f_\mathrm l}\Big),
\end{align}
where $T_k$ is the operator defined in 
\eqref{e:Tt}, $\mathrm x_t(f_\mathrm l)$ is defined in \eqref{eq:oldResult} 
with $f$ replaced with $f_\mathrm l$, $\tilde f_\mathrm s:=e^{\alpha(\tilde \beta - 1)} f_\mathrm s$, $\tilde f_\mathrm c:=e^{\alpha(\tilde \beta - 1)} f_\mathrm c$ and $\tilde f_\mathrm l := \sum_{p\in \mathbb Z^d_+: \alpha\tilde\beta>|p|b}e^{-(\alpha - |p|b)}\langle f_\mathrm l, \phi_p \rangle_\varphi \phi_p$.
	The following result is a special case of Theorem \ref{thm:M}.
\begin{thm}\label{thm: II}
	Under $\mathbb{\widetilde{P}}_{\mu}$, $R(t) \xrightarrow[t\rightarrow\infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l})$, where $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, and $\zeta^{f_\mathrm s},\zeta^{f_\mathrm c}$ and $\zeta^{-f_\mathrm l}$ are independent.
\end{thm}
\begin{proof}
	In this proof, we always work under $\mathbb{\widetilde{P}}_{\mu}$.
	According to the proof of 
\cite[Theorem 1.6]{RenSongSunZhao2019Stable} and the fact that the convergence in
 probability of random vectors to the zero vector is equivalent to the convergence of each components of the random vectors to zero, we have
\[
	R(t)-R'(t)
	\xrightarrow[t\to \infty]{\text{in probability}} 0.
\]
	With the help of Slutsky's theorem, what is left to show is that,
\begin{equation} \label{lem:UOT}
	R'(t)
	\xrightarrow[t\to \infty]{d}(\zeta^{f_\mathrm s},\zeta^{f_\mathrm c},\zeta^{-f_\mathrm l}).
\end{equation}

@@

%{
  	%\\&  = |-i|^{1+\beta} |(T_u f + t^{\tilde \beta -1} T_u f_\mathrm c)^{1+\beta} - (T_u f_\mathrm s)^{1+\beta} - (t^{\tilde \beta - 1}T_u f_\mathrm c)^{1+\beta}|
%}

@@

%{
	\\ \eta \int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm s)^{1+\beta}, \varphi \rangle  \mathrm du
	%- \eta 
	- \frac{1}{t} \eta 
	\int_0^{\lfloor t-\ln t \rfloor+1} \langle (-iT_u f_\mathrm c)^{1+\beta}, \varphi \rangle  \mathrm du\Big|
%}
